logbook simulations

### 2020-03-28 datasets/data_preprocessing.nb.Rmd
test hyperopt through shell script

# Write all test dataset files 
```{r}
# ace
write.csv(ace_test %>%  select(authors, title, abstract, keywords, label_included), "test_datasets/ace.csv")

@@

# write test dataset files for simulation (removing keywords)
```{r}
# ace
write.csv(ace_test %>%  select(authors, title, abstract, label_included), "sim_datasets/ace.csv")
# nudging (no keywords available)
write.csv(nudging_test %>% select(title, abstract, included), "sim_datasets/nudging.csv")
# ptsd
write.csv(ptsd_test %>% select(authors, title, abstract, included), "sim_datasets/ptsd.csv")
# hall (no keywords available )
write.csv(hall_test, "sim_datasets/software.csv")
# virus 
write.csv(v_test %>% select(authors, title, abstract, included), "sim_datasets/virus.csv")
# wilson
write.csv(w_test %>% select(authors, title, abstract, included), "sim_datasets/wilson.csv")
```

>>>>

# Write all test dataset files 
```{r, eval = FALSE}
# ace
write.csv(ace_test %>%  select(authors, title, abstract, keywords, label_included), "test_datasets/ace.csv")

@@

# write test dataset files for simulation (removing keywords)
```{r, eval = FALSE}
# ace
write.csv(ace_test %>%  select(authors, title, abstract, label_included), "sim_datasets/ace.csv")
# nudging (no keywords available)
write.csv(nudging_test %>% select(title, abstract, included), "sim_datasets/nudging.csv")
# ptsd
write.csv(ptsd_test %>% select(authors, title, abstract, included), "sim_datasets/ptsd.csv")
# hall (no keywords available )
write.csv(hall_test, "sim_datasets/software.csv")
# virus 
write.csv(v_test %>% select(authors, title, abstract, included), "sim_datasets/virus.csv")
# wilson
write.csv(w_test %>% select(authors, title, abstract, included), "sim_datasets/wilson.csv")
```

To check:
```{bash , eval = FALSE}
asreview stat test_datasets/*
```

returns 
```
************  ace.csv  ************

Number of papers:            2235
Number of inclusions:        41 (1.83%)
Number of exclusions:        2194 (98.17%)
Number of unlabeled:         0 (0.00%)
Average title length:        123
Average abstract length:     1623
Average number of keywords:  15.0
Number of missing titles:    0 (of which 0 included)
Number of missing abstracts: 0 (of which 0 included)

************  nudging.csv  ************

Number of papers:            1847
Number of inclusions:        100 (5.41%)
Number of exclusions:        1747 (94.59%)
Number of unlabeled:         0 (0.00%)
Average title length:        109
Average abstract length:     1831
Average number of keywords:  None
Number of missing titles:    0 (of which 0 included)
Number of missing abstracts: 0 (of which 0 included)

************  ptsd.csv  ************

Number of papers:            5031
Number of inclusions:        38 (0.76%)
Number of exclusions:        4993 (99.24%)
Number of unlabeled:         0 (0.00%)
Average title length:        104
Average abstract length:     1537
Average number of keywords:  9.9
Number of missing titles:    1 (of which 0 included)
Number of missing abstracts: 0 (of which 0 included)

************  software.csv  ************

Number of papers:            8896
Number of inclusions:        104 (1.17%)
Number of exclusions:        8792 (98.83%)
Number of unlabeled:         0 (0.00%)
Average title length:        81
Average abstract length:     896
Average number of keywords:  None
Number of missing titles:    0 (of which 0 included)
Number of missing abstracts: 0 (of which 0 included)

************  virus.csv  ************

Number of papers:            2304
Number of inclusions:        114 (4.95%)
Number of exclusions:        2190 (95.05%)
Number of unlabeled:         0 (0.00%)
Average title length:        103
Average abstract length:     1345
Average number of keywords:  20.3
Number of missing titles:    0 (of which 0 included)
Number of missing abstracts: 0 (of which 0 included)

************  wilson.csv  ************

Number of papers:            2333
Number of inclusions:        23 (0.99%)
Number of exclusions:        2310 (99.01%)
Number of unlabeled:         0 (0.00%)
Average title length:        83
Average abstract length:     1325
Average number of keywords:  31.3
Number of missing titles:    1 (of which 0 included)
Number of missing abstracts: 0 (of which 0 included)

### 2020-03-28 simulation_study/README.Rmd
test hyperopt through shell script

scp -r gerbrich@cartesius.surfsara.nl:/asreview/output/active/nb_max_random_triple_tfidf/ /Volumes/Gerbrich/asreview/archive/output

>>>>

scp -r gerbrich@cartesius.surfsara.nl:asreview/simulations/automated-systematic-review-simulations/scripts/output/active/nb_max_random_triple_tfidf ~

scp -r gerbrich@cartesius.surfsara.nl:asreview/simulations/automated-systematic-review-simulations/scripts/output/active/nb_max_random_triple_tfidf/ptsd_virus_ace_software_wilson_nudging/best ~
***
